%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------


\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended

\usepackage{fontspec}
\usepackage{fontawesome}


%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Justin}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Cartwright}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Fullstack Developer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{12}{Chicago, IL}\\
	\icon{Phone}{12}{+1 (740) 809-2278}\\
	\icon{At}{12}{\href{mailto:cartwright.76@gmail.com}{cartwright.76@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Github}{12}{\href{https://github.com/jcartw89}{github.com/jcartw89}}\\
	\icon{Medium}{12}{\href{https://medium.com/@cartwright.76}{cartwright.76}}\\
	\icon{Linkedin}{12}{\href{https://www.linkedin.com/in/justin-cartwright-54163426/}{justin-cartwright}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
Software Systems Engineer with over 10 years of experience ranging from front and backend cloud systems to data acquisition and processing as well as physics model simulation engines. Web development, embedded IoT systems, server motors, batteries, and engine control are some of the things I dabble in. A strong believer in first principles approaches to developing solutions for complex problems. 
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{React.js}{70}
		\baritem{JavaScript}{100}
		\baritem{Node.js}{100}
		\baritem{Python}{65}
		\baritem{Java}{75}
		\baritem{HTML/CSS}{65}
		\baritem{MySQL}{75}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{4/VSCode, 5/git, 4/Office, 4/Docker, 5/Linux}
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2018 -- Present}
		{Fullstack Developer}
		{Technicity LLC}
		{Develop fullstack cloud systems for IoT, enterprise,
		and startup applications. 
		Some notable examples include Knytt (\href{https://knytt.us}{knytt.us}),
		FoodForest (foodforest.app), and Iotery (iotery.io). 
		Work with a wide array of backend technologies, such as Express (Node.js),
		FastAPI (Python), and MySQL as well the React.js frontend framework.
		\\
		\texttt{Node.js}\slashsep\texttt{React.js}\slashsep\texttt{MySQL}\slashsep\texttt{Docker}\slashsep\texttt{AWS}\slashsep\texttt{Python}}
	\entry
		{2016 -- 2018}
		{Hardware Controls Interface Engineer}
		{Ford Motor Co.}
		{Drove controls software and calibration development for internal
		combustion engine EGR, VCT, and throttle body systems.
		Worked with development of embedded controls and diagnostics
		software as well as test automation. Co-authored five 
		automotive patents related to engine controls and vehicle to
		cloud communication. \\
		\texttt{C}\slashsep\texttt{MATLAB}\slashsep\texttt{CAN}\slashsep\texttt{Visual Basic}\slashsep\texttt{6-sigma}}
	\entry
		{2014 -- 2016}
		{Automotive Engineer}
		{Ford Motor Co.}
		{Worked in numerous roles in Ford's rotational program. Roles assumed include CAD design,
		simulation, testing, controls, and calibration. Developed and implemented mathematical models
		for proprietary performance simulation software.\\ 
		\texttt{Java}\slashsep\texttt{MATLAB}\slashsep\texttt{Excel}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2011 -- 2013}
		{Master's Degree in Mechanical Engineering}
		{The Ohio State Univeristy}
		{Research assistant under Prof. Ahmet Selamet at The Ohio State Center for Automotive Research. \\ 
		Master's Thesis: 
		\it{\href{https://etd.ohiolink.edu/!etd.send_file?accession=osu1385982535&disposition=inline}{The Characterization of an Externally Cooled Exhaust Manifold}}}
	\entry
		{2007 -- 2011}
		{Bachelor's Degree in Mechanical Engineering}
		{The Ohio State Univeristy}
		{\it{Summa Cumme Laude}}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}

	\textbf{English} - native \\
	\textbf{Portuguese} - fluent
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}

	I always love doing new things. 
	Some of my favorite activities include running, hiking, reading, 
	traveling, climbing, and of course coding.
	
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Interests}

	Machine Learning, 
	IoT systems, Investment Strategies, Foreign Languages and Cultures, 
	Photography, History, and Marketing. 
	
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
